---
title: "DSE3101_Week2"
author: "Tiffany"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read the file into R

```{r}
df <- readRDS("data/wk2_stocks.rds")
str(df)
```
## Statistics on S&P Prices

+ The cumulative returns of the S&P index during this period is `r round(sum(df$SPY_returns)*100, 2)`%

+ The average daily retuns of the S&P index during this period is `r round(mean(df$SPY_returns)*100, 2)`%

+ The standard deviation of the daily returns of the S&P index during this period is `r round(sd(df$SPY_returns)*100, 2)`%

## Plot of S&P Prices
```{r message = FALSE}
library(tidyverse)
ggplot(data=df, aes(x=date, y=SPY_prices)) +
  geom_line()
```

## Plot of Total Yearly Returns of S&P from 2001 to 2023
```{r message = FALSE}
df %>%
  mutate(year = year(date)) %>%
  filter(year <= 2023) %>%
  group_by(year) %>%
  summarize(yr_return = sum (SPY_returns)*100)%>%
  ggplot(aes(x=year, y=yr_return)) +
  geom_col()
  
```